\texttt{davos}: The Python package smuggler

### 2022-04-04 paper/main.tex
reframing motivation to include stability over time

% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
\section{Motivation and significance}
Modern open science practices encourage sharing code and data to enable others to explore, reproduce, learn from, and build upon existing work. Scientists, researchers, and educators produce many different forms of research-related code (e.g., experiments, data analyses, tutorials, demos) that they may seek to share with a wide range of audiences, including collaborators, students, the broader scientific community, and the general public. Python has become one of the most widely used and fastest-growing scientific programming languages by offering both powerful research functionality and high-level accessibility \cite{MullEtal15}. In addition to the language’s intuitive, readable grammar and large standard library, the Python ecosystem provides an extensive data science toolkit designed to facilitate rapid development and collaboration, including platforms for interactive programming (e.g., Project Jupyter, \cite{KluyEtal16}; Google Colaboratory), community-maintained libraries for data manipulation (e.g., \texttt{NumPy} \cite{HarrEtal20}, \texttt{SciPy} \cite{VirtEtal20}, \texttt{Pandas} \cite{McKi10}) and visualization (e.g., \texttt{Matplotlib} \cite{Hunt07}, \texttt{seaborn} \cite{Wask21}), and myriad other tools.

However, this also presents a challenge to sharing reproducible scientific Python code: different versions of a given package or library can behave differently, use different syntax, add or drop support for specific functions or other libraries, address (or introduce) bugs, and so on. While these issues are present to some extent in any language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages. Ensuring stable and reproducible results over time and across users therefore typically requires ensuring that shared code is always run with a specific set of versions for each package used.

>>>>

% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
\section{Motivation and significance}
An essential feature of software used in scientific research is that it behaves consistently every time it is run. For example, stable code can be crucial to ensuring constant conditions during data collection (e.g., across recordings, trials, or subjects) and that accurate, reliable outputs from statistical analyses. Additionally, modern open science practices encourage sharing code and data to enable others to explore, reproduce, learn from, and build upon existing work. Scientists, researchers, and educators produce many different forms of research-related code (e.g., experiments, analyses, tutorials, and demos) that they may seek to share with a wide range of audiences including collaborators, students, the broader scientific community, and the general public.

Python has become one of the most widely used and fastest-growing scientific programming languages by combining accessibility and readability with the availability of powerful research tools \cite{MullEtal15}. In addition to the language’s high-level, intuitive grammar and large standard library, the Python ecosystem provides an extensive data science toolkit designed to facilitate rapid development and collaboration, including platforms for interactive programming (e.g., Project Jupyter, \cite{KluyEtal16}; Google Colaboratory), community-maintained libraries for data manipulation (e.g., \texttt{NumPy} \cite{HarrEtal20}, \texttt{SciPy} \cite{VirtEtal20}, \texttt{Pandas} \cite{McKi10}) and visualization (e.g., \texttt{Matplotlib} \cite{Hunt07}, \texttt{seaborn} \cite{Wask21}), and myriad other tools.

However, this also presents a challenge to writing and sharing stable, reproducible scientific Python code: different versions of a third-party library can behave differently, use different syntax, add or drop support for specific functions or other libraries, address (or introduce) bugs, and so on. While these issues are present to some extent in any language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages. Ensuring consistent behavior over time and across users therefore typically requires ensuring that code is shared and run with a specific set of versions for each package used.
